Supplementary Material

### 2024-01-18 manuscript/supplement.qmd
add manuscript infrastructure

---
title: "Lactate transport inhibition therapeutically reprograms fibroblast 
    metabolism in experimental pulmonary fibrosis"

@@

format:
  docx:
    reference-doc: template.docx
    page-width: 7.5
    output-file: ziehr_2023_mcti_manuscript.docx
    fig-align: center

>>>>

---
title: "Supplementary Material"
subtitle: "Lactate transport inhibition therapeutically reprograms fibroblast 
    metabolism in experimental pulmonary fibrosis"

@@

format:
  docx:
    reference-doc: template.docx
    page-width: 7.5
    output-file: ziehr_2023_mcti_supplement.docx
    fig-align: center
